---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw04dwjkate

<!-- badges: start -->
<!-- badges: end -->

The goal of hw04dwjkate is to use two functions myseq_n() and seq_plot().

 1. myseq_n() function is for creating a recursive sequence defined by given formula.

 2. seq_plot() function is for creating a line plot of the output values of myseq_n() function.

## Installation

You can install the released version of hw04dwjkate by contacting "dj1997a@student.american.edu"

``` r
install.packages("hw04dwjkate")
```

## Test Example

```{r}
library(hw04dwjkate)
```


### Recursive Sequence

```{r}
myseq_n(x = c(2, 4, 3), n = 5)
myseq_n(x = c(2, 4, 3), n = 6)
myseq_n(x = c(2, 4, 3), n = 7)
```

### Sequence Plot

```{r}
my_data <- tibble::tribble(
  ~x, ~y, ~z, ~n,
  2,4,3,3,
  2,4,3,4,
  2,4,3,5,
  2,4,3,6,
  2,4,3,7,
  2,4,3,8,
  2,4,3,9,
  2,4,3,10,
  2,4,3,12)

seq_plot(my_data)
```



# Author Information

Author Name: Dawoon (Kate) Jung 

GitHub ID: dwjkate


